---
title: "p8105_hw1_pc2853"
author: "pc2853"
date: "September 21, 2018"
output: github_document
editor_options: 
  chunk_output_type: console
---
#Problem 1
```{r , include = FALSE}
library(tidyverse)
```

### Below is the dataset comprised of a numerical vector, a logical vector, a character vector and a factor vector, with the mean of each vector shown.
```{r }
hw1_df = tibble(
 vec_numeric = runif(10, min = 0, max = 5),
 vec_logical = c(vec_numeric > 2),
 vec_char = c("My", "Name", "Is", "Pengxuan", "Chen", "Thisis", "My", "First", "Homework", "Assignment"),
 vec_factor = factor(c("coke", "pepsi", "coke", "coke", "pepsi", "coke", "coke", "coke", "coke", "coke")),
)


mean(hw1_df$vec_numeric)
mean(hw1_df$vec_logical)
mean(hw1_df$vec_char)
mean(hw1_df$vec_factor)
```

### Here is the code converting the type of vectors into another without showing the results.
```{r results = "hide", warning=FALSE}
as.numeric(hw1_df$vec_logical)
as.numeric(hw1_df$vec_char)
as.numeric(hw1_df$vec_factor)
```

```{r results = "hide", warning=FALSE}
as.numeric(as.factor(hw1_df$vec_char))
as.numeric(as.character(hw1_df$vec_factor))
```


---
# Problem 2
```{r setup, include = FALSE}
library(tidyverse)
```


```{r}
set.seed(1234)

hw1_df2 = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec_logical = c((x + y) > 0),
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```
### Here is a data frame comprised of 2 random samples x and y from standard normal distribution, and a logical vector, numerical vector and a factor vector.

* The size of the dataset is `r nrow(hw1_df2)`
* The mean of the dataset is `r mean(hw1_df2$x)`
* The median of the dataset is `r mean(hw1_df2$x)`
* The proportion of cases for which the logical vector is TRUE, is `r length(hw1_df2$vec_logical[hw1_df2$vec_logical == "TRUE"])`
```{r}

```


### Below are the scatterplots of y vs x which are colored by using logical, numerical and factor vectors separately.
```{r}
ggplot(hw1_df2, aes(x=x, y=y, color = hw1_df2$vec_logical)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)

ggplot(hw1_df2, aes(x=x, y=y, color = hw1_df2$vec_factor)) + geom_point()
ggplot(hw1_df2, aes(x=x, y=y, color = hw1_df2$vec_numeric)) + geom_point()

```

